---
title: "Example Data Scavenger Hunt"
author: "Ted Laderas"
date: "January 11, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## What is a Data Scavenger Hunt?

A Data Scavenger Hunt is an activity that gets people to explore data. The `burro` app serves as a simple entry point to exploring the data.  

There are multiple key elements of data scavenger hunts:

1. Find a Dataset and build the app
1. Have an overarching research question
1. Have a set of increasingly complex questions about the data for people to answer
1. Quick intro session
1. Divide the participants into groups and assign questions
1. Have recaps where participant groups show each other how they answered the question

We highly recommend having a [Code of Conduct](https://biodataclubkit.github.io/code_of_conduct/) for these sessions.

## Have a Dataset

This is the most important part! 

Check out [Building a burro app](https://laderast.github.io/burro/articles/making_a_burro_app.html) on how to build your app.

We're going to use the NHANES (National Health and Nutrition Examination Survey) dataset package as our dataset. 

```{r eval=FALSE}
install.packages("NHANES")
```

Load it up and take a look at the documentation for this dataset:

```{r}
library(NHANES)
data(NHANES)
?NHANES
```

## Have a Research Question

The research question will focus the exploration of the data by deciding an outcome. For the NHANES data, we want to focus on Depression. In the `NHANES` dataset, Depression is represented as the `Depressed` variable.

## Data Scavenger Hunt Questions

In designing the questions you will use in the scavenger hunt, you should do some prework and explore the dataset. This will inform your questions that you ask participants to look for.

Try and map the complexity of the questions to the three menu items: 
