---
title: "Example Data Scavenger Hunt"
author: "Ted Laderas"
date: "January 11, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## What is a Data Scavenger Hunt?

A Data Scavenger Hunt is an activity that gets people to explore data. The `burro` app serves as a simple entry point to exploring the data.  

There are multiple key elements of data scavenger hunts:

1. Find a Dataset and build the app
1. Have an overarching research question
1. Have a set of increasingly complex questions about the data for people to answer
1. Quick intro session
1. Divide the participants into groups and assign questions
1. Have recaps where participant groups show each other how they answered the question

We highly recommend having a Code of Conduct for these sessions.

## 1. Have a Dataset



## Data Scavenger Hunt Questions




```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
